Classifying Human Driving Behavior via Deep Neural Networks

### 2017-06-08 presentation/presentation.tex
added figures to presentation slides

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{frame}
\frametitle{Problem Statement}
\begin{itemize}
\item Modern car systems collect real-time data of the car status and driving behavior of the driver
\item Those data is worth for healthcare and research
\item Using driving behavior data to diagnose medical conditions
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Project Background}
\begin{itemize}
\item Classify driving simulation data from novice and expert drivers using several different neural network models
\item Explain LSTM and Auto-encoder
\item Compare result from three different neural network models
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item An artificial neuron has input signals, weights, bias, and activation function
\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Data Set}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Data Set}
\begin{itemize}
\item Collected in the high-fidelity simulator of the Center for Injury Research Prevention Studies at the \textit{Children's Hospital of Philadelphia} (CHOP)
\item 16 traces = 4 tracks $\times$ (2 expert drivers + 2 inexpert drivers)
\item 100 features collected at 60Hz
	\begin{itemize}
	\item Car status: velocity, steer, Brake, throttle and etc.
	\item Environment status: current speed limit, and etc.
	\item instruction: left turn, right turn, and etc.
	\end{itemize}
\item Two datasets
	\begin{itemize}
	\item {\em raw dataset}: 98 features without time stamps
	\item {\em filtered dataset}: 23 features - more important features from 100 features
	\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Data Size}
\begin{itemize}
\item The number of samples in trace

From result of experiment with different re-sampled periods, more densely re-sampled data gives better performance

\item The number of traces

12 traces are not enough to train proposed neural networks

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Limitation of Auto-encoders}
\begin{itemize}
\item No optimize transfer matrices

When Auto-encoder tries to reduce dimensions, if encoder and decoder transfer matrices are not exist, encoded data has noise. It can make hard to train following neural networks.

\item Always try to keep all information

Auto-encoder does not ignore or exclude unimportant features

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Problem in training MAE}
\begin{itemize}
\item Training time

Processing of pretraining takes long time

\item Learn error from previous layer during pretraining

Fix previous layer while follow auto-encoder layer is trained

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{itemize}
\item Experiment with more traces
\item Research auto-encoder that accept some form of supervision and reduce dimensions with the ability to ignore unimportant features and keep information from the important features
\item Try different way to train MAE
\end{itemize}
\end{frame}

@@

%\begin{frame}[allowframebreaks]
%\frametitle{References}
%\bibliographystyle{amsalpha}
%\bibliography{../paper/references.bib}
%\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{frame}
\frametitle{Problem Statement}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.85\textwidth]{project-overall}
%    \caption{General Artificial Neuron}
    \label{fig:diagnosticdriving}
\end{figure}
\begin{itemize}
\item Modern car systems collect real-time data of the car status and driving behavior of the driver
\item Such data is very valuable for healthcare and research
\item {\color{blue} Goal}: use driving behavior data to diagnose medical conditions
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Project Background}
\begin{itemize}
\item Work in the context of the NSF SCH {\em Diagnostic Driving} project
\item Partners:
	\begin{itemize}
	\item Drexel University (lead)
	\item Children's Hospital of Philadelphia (CHOP)
	\item George Mason University
	\item University of Central Florida
	\end{itemize}
\item CHOP and GM are in charge of data collection, and Drexel and UCF are in charge of machine learning
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Project Tasks}
\begin{itemize}
\item Learn and understand LSTM and Auto-encoders neural networks
\item Classify driving simulation data from novice and expert drivers using several different neural network models
\item Compare result from three different neural network models created specifically for this task
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item An artificial neuron has input signals, weights, bias, and activation function \cite{raschka2015python}
\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Data Set}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{figure-simulator-cropped}
    \caption{Driving Simulator at CHOP}
    \label{fig:simulator}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Data Set}
\begin{itemize}
\item Collected in the high-fidelity simulator of the Center for Injury Research Prevention Studies at the \textit{Children's Hospital of Philadelphia} (CHOP)
\item 16 traces = 4 tracks $\times$ (2 expert drivers + 2 inexpert drivers)
\item 100 features collected at 60Hz
	\begin{itemize}
	\item Car status: velocity, steer, Brake, throttle and etc.
	\item Environment status: current speed limit, and etc.
	\item instruction: left turn, right turn, and etc.
	\end{itemize}
\item Two datasets
	\begin{itemize}
	\item {\em raw dataset}: 98 features without time stamps
	\item {\em filtered dataset}: 23 features - more important features from 100 features
	\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Data Size}
\begin{itemize}
\item The number of samples in trace:

From the result of experiments with different re-sampled periods, more densely re-sampled data gives better performance

\item The number of traces:

12 traces are not enough to train the proposed neural networks

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Limitation of Auto-encoders}
\begin{itemize}
\item No optimize transfer matrices:

When Auto-encoder tries to reduce dimensions, if encoder and decoder transfer matrices do not exist, encoded data has noise. It can make it hard to train subsequent neural networks.

\item Always try to keep all information:

Auto-encoder does not ignore or exclude unimportant features (it's unsupervised)

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Problem in training MAE}
\begin{itemize}
\item Training time:

Processing of pretraining takes a long time

\item Learn error from previous layer during pretraining:

Fix previous layer while the following auto-encoder layer is trained

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{itemize}
\item Experiment with more traces
\item Research auto-encoder that accept some form of supervision and reduce dimensions with the ability to ignore unimportant features and keep information from the important features (and that can be used for sequential data with LSTMs)
\item Try different ways to train MAE
\end{itemize}
\end{frame}

@@

\begin{frame}[allowframebreaks]
\frametitle{References}
\bibliographystyle{amsalpha}
\bibliography{../paper/references.bib}
\end{frame}
